DNA Methylation Analyses

### 2023-02-16 DNA-methylation.Rmd
meth - formatting

This will create deduplicated.bismark.cov.gz, uncompressed is in this format. And while a bedGraph file is generated, in this workflow a bedGraph will be generated later that uses information from merged strands (as opposed to this output).

@@

Column organization

@@

A genome-wide cytosine report ins generated, with this code as an example:

@@

#Generating files for downstream analysis

From here it could be useful to do some simple file reorganizaion to obtain bedgraph or tab files for down stream analysis.

@@

It is often useful to sort files for downstream analysis (eg methylkit, IGV)

>>>>

This will create a file with the suffix `deduplicated.bismark.cov.gz` (example shown below in uncompressed format). And while a bedGraph file is generated, in this workflow a bedGraph will be generated later that uses information from merged strands (as opposed to this output).

@@

column organization of the file

@@

A genome-wide cytosine report is generated, with this code as an example:

@@

# Generating files for downstream analysis

From here it could be useful to do some simple file reorganizaion to obtain bedgraph or tab files for downstream analysis (eg bedtools, GLMs).

@@

It is sometimes useful to sort BAM files for downstream analysis (eg methylkit, IGV)
